Light-Light Scattering: Feynman Diagrams

### 2022-12-13 latex/PHYS441/paper.tex
add articles

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\linewidth]{Feynman-diagram.png}
	\caption{Feynman diagrams for light-light scattering.}
	\label{fig:light-light-scattering-feynman}
\end{figure}

@@

@@

\end{document}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{biblatex}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\linewidth]{figures/Feynman-diagram.png}
	\caption{Feynman diagrams for light-light scattering.}
	\label{fig:light-light-scattering-feynman}
\end{figure}

@@

\subsection{ATLAS Observation}
Light-by-light scattering is a very rare phenomenon in which two photons – particles of light – interact,
producing another pair of photons. This process was among the earliest predictions of quantum electrodynamics (QED),
the quantum theory of electromagnetism, and is forbidden by classical physics theories (such as
Maxwell's theory of electrodynamics).

Direct evidence for light-by-light scattering at high energy had proven elusive for decades, until the Large Hadron
Collider (LHC) began its second data-taking period (Run 2). Collisions of lead ions in the LHC
provide a uniquely clean environment to study light-by-light scattering. Bunches of lead ions that are accelerated to
very high energy are surrounded by an enormous flux of photons. Indeed, the coherent action from the large number of
82 protons in a lead atom with all the electrons stripped off (as is the case for the lead ions in the LHC)
give rise to an electromagnetic field of up to 1025 Volt per metre. When two lead ions pass close by each
other at the centre of the ATLAS detector, but at a distance greater than twice the lead ion radius, those
photons can still interact and scatter off one another without any further interaction between the lead ions, as the reach of
the (much stronger) strong force is bound to the radius of a single proton. These interactions are
known as ultra-peripheral collisions.

`The ATLAS Collaboration has reported the observation of light-by-light scattering with a significance
beyond 8 standard deviations.`

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.5\linewidth]{figures/LbyL-fig2.png}
	\caption{Invariant mass distribution of the measured final state photon pairs (markers), compared
		to the expected light-by-light scattering signal (red line) and expected background contributions
		(shaded areas). (Image: ATLAS Collaboration/CERN)}
	\label{fig:Atlas data}
\end{figure}

In a result published in Nature Physics in 2017, the ATLAS Collaboration found thirteen candidate events for light-by-light scattering in lead-lead collision data recorded in 2015, for 2.6 events expected from background processes. The corresponding significance of this result was 4.4 standard deviations – making it the first direct evidence of high-energy light-by-light scattering.

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.7\linewidth]{figures/EventDisplay_LbyL.png}
	\caption{ATLAS event display showing the energy deposits of two photons in the electromagnetic
		calorimeter (green) on opposite sides and no other activity in the detector, which is the clean signature
		of light-by-light scattering. The Feynman diagram of this process is shown in the lower right corner.
		(Image: ATLAS Collaboration/CERN)}
	\label{fig:Atlas_event}
\end{figure}

\subsection{Light-by-Light Scattering at Low Energies}%

\subsection{Positron Production in Multiphoton Light-by-Light Scattering}%
\label{subsec:positron}

\label{subsec:light-light-low-energy}
A signal of 106±14 positrons above background has been observed in collisions of a low-emittance 46.6 GeV electron beam with terawatt pulses from a Nd:glass laser at 527 nm wavelength in an experiment at the Final Focus Test Beam at SLAC. The positrons are interpreted as arising from a two-step process in which laser photons are backscattered to GeV energies by the electron beam followed by a collision between the high-energy photon and several laser photons to produce an electron-positron pair. These results are the first laboratory evidence for inelastic light-by-light scattering involving only real photons.

@@

    \printbibliography
\end{document}
